Figures

### 2019-07-03 figures/06_lulc_buffer_demo.Rmd
add total ag panel, closes #15

test <- raster::mask(nlcd, iws) %>% 
  as.data.frame(xy = TRUE) %>%
  dplyr::select(x, y, contains("Value"))
test <- test[test[,3] %in% c(81, 82),]
test[,3] <- factor(test[,3])
names(test)[3] <- "value"
test <- test %>%
  drop_na("value")
cols <- dplyr::filter(pal_nlcd(), code %in% unique(test[,3]))

@@

g_nlcd <- ggplot() + 
  geom_raster(data = test, aes(x = x, y = y, fill = value)) +
  scale_fill_manual(values = cols$color, labels = cols$description) +
  geom_sf(data = iws, alpha = 0) +
  coord_sf(datum = NA) + 
  theme_void() + 
  theme(legend.position = 0)

g_cdl <- ggplot() + 
  geom_raster(data = dplyr::filter(cdl_df, as.character(category) %in% 
                                     c("corn", "soybeans", "pasture")), 
              aes(x = x, y = y, fill = category)) +
  scale_fill_manual(values = setNames(color_key$color, 
                                      color_key$category)) +
  geom_sf(data = iws, alpha = 0) +
  geom_sf(data = network) +
  geom_sf(data = ll_lake) +
  coord_sf(datum = NA) + 
  theme_void()

cowplot::plot_grid(g_nlcd + ggtitle("NLCD (2011)"), 
                   g_cdl + ggtitle("CDL (2010)"), 
                   rel_widths = c(0.75, 1))
```

>>>>

test <- raster::mask(nlcd, iws) %>% 
  as.data.frame(xy = TRUE) %>%
  dplyr::select(x, y, contains("Value"))
test <- test[test[,3] %in% c(81, 82),]
test[,3] <- factor(test[,3])
names(test)[3] <- "value"
test <- test %>%
  drop_na("value")
cols     <- dplyr::filter(pal_nlcd(), code %in% unique(test[,3])) %>%
  mutate(description = c("Pasture", "Row Crops"))
cols_agg <- mutate(cols, color = "#AA7028", description = "Total Ag")[2,]

@@

g_nlcd_agg <- ggplot() + 
  geom_raster(data = mutate(test, value = 82), aes(x = x, y = y, fill = as.factor(value))) +
  scale_fill_manual(values = cols_agg$color, labels = cols_agg$description) +
  geom_sf(data = iws, alpha = 0) +
  geom_sf(data = network) +
  geom_sf(data = ll_lake) +
  coord_sf(datum = NA) + 
  labs(fill = "") +
  theme_void() # + 
  # theme(legend.position = 0)

g_nlcd <- ggplot() + 
  geom_raster(data = test, aes(x = x, y = y, fill = value)) +
  scale_fill_manual(values = cols$color, labels = cols$description) +
  geom_sf(data = iws, alpha = 0) +
  geom_sf(data = network) +
  geom_sf(data = ll_lake) +
  coord_sf(datum = NA) + 
  labs(fill = "") +
  theme_void() # + 
  # theme(legend.position = 0)

cdl_df <- mutate(cdl_df, category = forcats::fct_collapse(cdl_df$category, 
                                                        `Corn` = "corn", 
                                                        `Soybeans` = "soybeans", 
                                                        `Pasture` = "pasture"))
g_cdl <- ggplot() + 
  geom_raster(data = dplyr::filter(cdl_df, as.character(category) %in% 
                                     c("Corn", "Soybeans", "Pasture")), 
              aes(x = x, y = y, fill = category)) +
  scale_fill_manual(values = 
                      setNames(
                        color_key$color, 
                        snakecase::to_any_case(color_key$category, "sentence"))
    ) +
  geom_sf(data = iws, alpha = 0) +
  geom_sf(data = network) +
  geom_sf(data = ll_lake) +
  coord_sf(datum = NA) + 
  labs(fill = "") +
  theme_void()

cowplot::plot_grid(
  g_nlcd_agg + ggtitle("Total Ag"), 
  g_nlcd + ggtitle("Row Crops"), 
  g_cdl + ggtitle("Individual Crops"), 
                   rel_widths = c(0.95, 1, 0.95), nrow = 1)
```
